Expanding the Popularity of the NHL Through Increased Goal Scoring

### 2023-04-05 outputs/paper/paper.qmd
fix

---
title: "Expanding the Popularity of the NHL Through Increased Goal Scoring"
subtitle: "An Analysis of the Increase in Goal Scoring During from 2011 to 2023"
author: 
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/thejasonminh/nhlpoints"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "Of the four major sports in the USA, the NHL is the least popular. In an effort to grow the game and make the game more exciting, the NHL wanted to increase goal scoring. Using data from the NHL, the paper will use graphs and tables to analyze average leaguewide goal scoring per game from the 2011-2012 to 2022-2023 seaons. A linear regression model will also be created to predict goal scoring averages in the upcoming seasons. Results show that the NHL was succesful in their mission as the average goals per game increased per season, with the current season exhibiting the highest average goals per game in a 10 year period. These findings suggest that factors such as increased player talent, more penalties and rule changes have resulted in more goals scored every season. To further grow the game, analysis on the topic of matchups, streaming, and media narratives is recommended."
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Expanding the Popularity of the NHL Through Increased Goal Scoring"
subtitle: "An Analysis of the Increase in Goal Scoring From 2011 to 2023"
author: 
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/thejasonminh/nhlpoints"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "Of the four major sports in the USA, the NHL is the least popular. In an effort to grow the game and make the game more exciting, the NHL wanted to increase goal scoring. Using data from the NHL, the paper will use graphs and tables to analyze average leaguewide goal scoring per game from the 2011-2012 to 2022-2023 seaons. A linear regression model will also be created to predict goal scoring averages in the upcoming seasons. Results show that the NHL was succesful in their mission as the average goals per game increased per season, with the current season exhibiting the highest average goals per game in a 10 year period. These findings suggest that factors such as increased player talent, more penalties and rule changes have resulted in more goals scored every season. To further grow the game, analysis on the topic of matchups, streaming, and media narratives is recommended."
number-sections: true
bibliography: references.bib
---
